\subsection{A*}

\subsubsection{Intuition}
A* is a best-first search algorithm that explores the most promising partial assignments first, guided by a cost function.

\subsubsection{Heuristics}
To guide the search efficiently, A* uses a heuristic function $h(n)$ that estimates the "cost to goal" from a given partial assignment. The total cost function is defined as:
\[
f(n) = g(n) + h(n)
\]
where:
\begin{itemize}
  \item $g(n)$ is the actual number of variables assigned so far (the path cost).
  \item $h(n)$ is the estimated number of unsatisfied clauses.
\end{itemize}

Several heuristics can be used:

\begin{itemize}
  \item \textbf{Clause-based heuristic:} Count the number of clauses that are currently unsatisfied under the partial assignment.

  \item \textbf{Optimistic heuristic:} Count only clauses that are fully assigned and violated. This makes the heuristic admissible and allows for more exploration.

  \item \textbf{Graph-based penalty (optional):} Add a penalty for partial solutions that look disconnected or under-connected, so the algorithm can be more likely to have globally connected configurations.
\end{itemize}

\subsubsection{Implementation}

\begin{enumerate}
  \item \textbf{Generate variables:} Represent all possible bridges between islands using Boolean variables.

  \item \textbf{Add constraints:} Encode logical conditions into CNF clauses:
  \begin{itemize}
    \item No duplicate bridges.
    \item Degree of each island must match its number.
    \item No crossing bridges.
  \end{itemize}

  \item \textbf{Initialize priority queue:} Start with an empty assignment and compute its $f(n)$ value.

  \item \textbf{Search loop:}
  \begin{enumerate}
    \item Pop the assignment with the smallest $f(n)$ from the priority queue.
    \item If all variables are assigned and all clauses are satisfied, and the resulting graph is connected, return the solution.
    \item Otherwise, pick one unassigned variable and expand the current state by assigning it both \texttt{True} and \texttt{False}.
    \item For each expanded state, compute $f(n)$ and push it into the priority queue.
    \item Optionally skip states that already violate a clause under full assignment.
  \end{enumerate}

  \item \textbf{Fail case:} If the priority queue is exhausted without finding a solution, report failure.
\end{enumerate}
